results

### 2020-08-13 analysis/results.Rmd
paratext recognition oa articles

---
title: "results"
author: "Najko Jahn"
date: "7/7/2020"
bibliography: references.bib
csl: chicago.csl
output: github_document
---

@@

@@

hybrid_df <- els_tdm %>% 
  select(doi, URL) %>% 
  inner_join(invoice_df, by = c("URL" = "tdm_url")) %>% 
  select(-URL) %>% 
  inner_join(hybrid_md, by = c("doi")) %>% 
  distinct()
```

>>>>

---
bibliography: references.bib
csl: chicago.csl
output: github_document
---

@@

```{r}
# paratext pattern
para <- c('^Author Index$|^Back Cover|^Contents$|^Contents:|^Cover Image|^Cover Picture|^Editorial Board|^Front Cover|^Frontispiece|^Inside Back Cover|^Inside Cover|^Inside Front Cover|^Issue Information|^List of contents|^Masthead|^Title page')
```

@@

hybrid_df <- els_tdm %>% 
  select(doi, URL) %>% 
  inner_join(invoice_df, by = c("URL" = "tdm_url")) %>% 
  select(-URL) %>% 
  inner_join(hybrid_md, by = c("doi")) %>% 
  distinct() %>%
  filter(!grepl(para, title))

flipped_jns_df <-
  els_jns %>%
    filter(issn %in% flipped_jns$issn)
```
